% English CV of Tom M. Ragonneau (05/05/2020).
\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,academicons]{altacv}
%% AltaCV uses the fontawesome and academicon fonts and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\setmainfont{Lato}

\definecolor{Mulberry}{HTML}{0F4C81}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Mulberry!70!black}
\colorlet{accent}{Mulberry}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{TOM M. RAGONNEAU}
\tagline{Ph.D. Student, Computational Mathematics and Optimization}
% \photo{2.8cm}{Globe_High}
\personalinfo{%
    % Not all of these are required!
    \email{tom.ragonneau@connect.polyu.hk}
    \mailaddress{P115, Mong Man Wai Bldg., The Hong Kong Polytechnic University}
    \location{Hong Kong}
    \homepage{www.tom-ragonneau.co}
%    \twitter{@twitterhandle}
%    \linkedin{linkedin.com/in/yash-raj-579b96156/}
    \github{github.com/TomRagonneau}
    \orcid{orcid.org/0000-0003-2717-2876}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\cvsection[page1sidebar]{Education}

\cvevent{Ph.D. Student in Computational Mathematics}{The Hong Kong Polytechnic University}{Sep. 2019 -- Ongoing}{Hong Kong}
\begin{itemize}
    \item Department of Applied Mathematics.
    \item Supervised by Dr. Zaikun Zhang and Prof. Xiaojun Chen.
    \item Supported by the Research Grants Council (RGC) of Hong Kong, under the Hong Kong Ph.D. Fellowship Scheme (HKPFS).
\end{itemize}

\divider

\cvevent{M.Sc. Degree in Scientific Computing}{Toulouse INP, E.N.S.E.E.I.H.T.}{Sep. 2018 - Jul. 2019}{Toulouse, France}
\begin{itemize}
    \item Graduated in Performance in Software, Media and Scientific Computing (PSMSC).
    \item GPA: 4.0
\end{itemize}

\divider

\cvevent{M.Eng. Degree in HPC and Big Data}{Toulouse INP, E.N.S.E.E.I.H.T.}{Sep. 2016 - Jul. 2019}{Toulouse, France}
\begin{itemize}
    \item Department of Computer Science and Applied Mathematics.
    \item Majoring in optimization, HPC and machine learning.
    \item GPA: 3.9
\end{itemize}

\cvsection{Working Experience}

\cvevent{Research Assistant}{The Hong Kong Polytechnic University}{Mar 2019 -- Sep. 2019}{Hong Kong}
\begin{itemize}
    \item Department of Applied Mathematics.
    \item M.Eng. final-year internship.
\end{itemize}

\divider

\cvevent{Machine Learning Research}{Toulouse INP, E.N.S.E.E.I.H.T. \& ALTRAN}{Jan. 2019 -- Mar. 2019}{Toulouse, France}
\begin{itemize}
    \item Deep learning approach for estimation of the nearshore bathymetry.
    \item M.Eng. final-year project.
\end{itemize}

\divider

\cvevent{Machine Learning Engineering}{Axians Cloud Builder}{Jun. 2018 -- Sep. 2018}{Toulouse, France}
\begin{itemize}
    \item Prediction of the load of an HPC cluster (National Centre for Space Studies) managed by GPFS via machine learning tools.
    \item M.Eng. second-year internship.
\end{itemize}

\end{document}
